Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-06 WSSSPE3/report/WSSSPE3_review.tex
Matthias Bussonnier's talk

\item \textbf{Matthias Bussonnier: \textit{User Data Collection in Open Source}}

>>>>

\item \textbf{Matthias Bussonnier: \textit{User Data Collection in Open Source}}
This talk highlighted an attempt to solve the common problem for open source
development that it is difficult to collect information about how many people
use the software, how often, which version, which parts of the software, or on
which operating system. Current solutions include surveys, but these have high
uncertainties. A different approach is based on automatic ``call-backs'' that
collect these information at run-time and send it to a central place for
analysis. Problems with this approach include obtaining agreement from the
user, legal issues, increased maintenance (servers), ethical questions, but
also the lack of a common infrastructure. Some of these problems are of social
nature and have to be solved as such, but especially the last problem of a
missing common infrastructure is attacked byt the sempervirens project, which
provides common APIs and a library implementation for common, repeating tasks
like obtaining user consent. Results are uploaded not directly to project
servers, but to neutral third parties that only publish aggregated statistics
to projects. Sempervirens can be found on github~\footnote{github:njsmith/sempervirens}.
